% ______________________________________________________________________________
%
%   1DV600 - Software Technology
%   Assignment 1 -- "Personal planning, Vision and Project Plan"
%
%  Author:  Jonas Sjöberg
%           Linnaeus University
%           js224eh@student.lnu.se
%           https://github.com/jonasjberg
%
%    Date:  2017-02-01 -- 2017-02-05
%
% License:  Creative Commons Attribution 4.0 International (CC BY 4.0)
%           <http://creativecommons.org/licenses/by/4.0/legalcode>
%           See LICENSE.md for additional licensing information.
% ______________________________________________________________________________


% ______________________________________________________________________________
\section{Task 3 -- Project Plan}\label{task-3}

\paragraph{Instructions}\label{task-3-instructions}
from the course Wiki\cite{1dv600:lab1:instructions}:

\begin{quote}
  Write a project plan for the project. This project plan should show the way
  to the complete and finished application, something that you should be able
  to follow. Write as much as possible in the project plan, add the
  milestones from Assignment Overview, and update the document throughout the
  course when you know more in the later assignments.  Again, as an addition,
  write down your reflections on creating a project plan. This reflection
  should be about 100 words.
\end{quote}


% ______________________________________________________________________________
\subsection{Project Plan}\label{task-3-project-plan}

\subsubsection{Overarching Goals}\label{task-3-goals}
The main overarching goal of the project is to produce a simple library system
for managing a collection of books.

Starting points:

\begin{enumerate}
  \item Fix bugs in the build system. Currently, I am unable to redeploy
        without restarting the virtual machine that runs the web server, which
        is completely unacceptable.
  \item Research the frontend source code to better understand how exceptions
        seem to be thrown for simple errors in the \texttt{JSON} data, like
        stray commas and whitespace.
  \item Develop classes to act as containers for all metadata fields,
        eliminating use of primitive data types to storage book metadata.
  \item Continously adjust and re-evaluate during continous integration as
        problems occur when connecting the code being developed with the
        given front-end code.
\end{enumerate}

I will initially focus mainly on the above issues. The project plan is thus
expected to change drastically during development.


\subsubsection{Planning Strategy}
I will initially focus primarily on these main points. More detailed planning
currently barely seems worthwhile as the overarching starting points are very
likely to shift or change rapidly.
Additionally, I lack serious experience with web development in general.  And
in particular the build system \texttt{gradle} \cite{tool:gradle}, the
\texttt{VirtualBox} \cite{virtualbox:vdidetails} wrapper \texttt{Vagrant} and
the provided front-end based on the \texttt{dropwizard}
\cite{framework:dropwizard} framework.

So I am not able to produce a valid long-term plan. The project has no choice
but to adopt a more ``agile'' approach.

I will adopt an iterative, agile approach -- short concise changes and constant
re-evaluation of the planning.
