\section{Task 1 -- Personal Planning}\label{task-1-personal-planning}

\subsection{Instructions}\label{instructions}

\begin{quote}
When the client requests a list of books to present for the user it does
the call \texttt{http://localhost:9090/api/books/} to the server and it
expects the answer as a JSON object (an associative array). We are going
to split the functionality into three tasks, but it is your task to plan
these tasks. Take into account the time for learning and understanding
of the problem when you plan the time. Make your planning with 15
minutes as the minimum unit. Repeat the following pattern for all
subtasks (A, B, C):

\begin{itemize}
\tightlist
\item
  Plan
\item
  Implement
\item
  Reflect
\end{itemize}

Each subtask should be documented with at least 100 words.
\end{quote}

\subsection{Subtask A -- Books}\label{subtask-a-books}

\subsubsection{Instructions}\label{instructions-1}

\begin{quote}
The main objective of the subtask is to create a list of books and a
function or method to get them. There are slight differences depending
on which implementation you are using, either Java or Node.js but those
differences will be clearly noted. Common for both is that they should
handle books, and for each book we need the information id, title,
author, genre, publish date, price and description.

\mbox{}%
\subparagraph{Java}\label{java}

Create a class in the package ``models'' that represents a book. After
that, create a short list of fictive (or real) objects in the function
getBooks that is available in GetBooksResource. When calling the URL
http://localhost:9090/api/books the list of books should be outputted
with System.out.println. The subtask is done when you see the objects in
the terminal (where vagrant is run).
\end{quote}

\subsubsection{Plan}\label{plan}

The \texttt{book} class is a critical datatype that will be used
throughout the software. As such, the class should be extendable and
designed according to the ``{[}open/closed principle{]}{]}'',

The class must meet the following requirements:

\begin{itemize}
\tightlist
\item
  Encapsulate the information needed to describe books contained in the
  system

  \begin{itemize}
  \tightlist
  \item
    Id
  \item
    Title
  \item
    Author
  \item
    genre
  \item
    Date of publication
  \item
    price
  \item
    Description
  \end{itemize}
\end{itemize}

\subsubsection{Implement}\label{implement}

\subsubsection{Reflect}\label{reflect}

\subsection{Subtask B -- JSON}\label{subtask-b-json}

\subsubsection{Instructions}\label{instructions-2}

\begin{quote}
Convert the objects created in subtask a into an JSON object and show it
in the terminal using either System.out.println(Java) or console.log
(Node.js).

\mbox{}%
\subparagraph{Improvement Strategies}\label{improvement-strategies}

Choose two improvement strategies based on your reflections on subtask a
and b. Describe what you have decided to improve and why. Implement your
improvements in the next subtask.
\end{quote}

\subsection{Subtask C -- Web}\label{subtask-c-web}

In this subtask you are to answer the request in the web browser instead
of printing it to the terminal. The subtask is done when you see the
JSON object on screen. For inspiration, have a look at PingResource that
you find in the same folder as the GetBooksResource. If you follow the
\href{https://htmlpreview.github.io/?https://github.com/tobias-dv-lnu/1dv600-lab/blob/master/api-specification/api-specification.html}{API
for the model} (as seen in
\href{https://htmlpreview.github.io/?https://github.com/tobias-dv-lnu/1dv600-lab/blob/master/api-specification/api-specification.html\#books-get}{GET
api/books})​, you will be able to show the books in the list.
